ZPY: Open Source Synthetic Data for Computer Vision

### 2021-06-22 docs/paper/paper.tex
more progress

@@

@@

@@

@@

Package detection
Effect of domain randomized lighting
Effect of domain randomized backgrounds
Pre-training w/ real and fine-tuning on synthetic
The Cost of Synthetic Data
Comparison to Data Labeling

\subsection{Lists}
\begin{itemize}
	\item Background material and texture.
	\item Lighting intensity and positioning.
	\item Object material and texture.
	\item Number of objects in view.
\end{itemize}

See results in the Table~\ref{tab:table}.

\begin{table}
	\caption{Sample table title}
	\centering
	\begin{tabular}{lll}
		\toprule
		\multicolumn{2}{c}{Part}                   \\
		\cmidrule(r){1-2}
		Name     & Description     & Size ($\mu$m) \\
		\midrule
		Dendrite & Input terminal  & $\sim$100     \\
		Axon     & Output terminal & $\sim$10      \\
		Soma     & Cell body       & up to $10^6$  \\
		\bottomrule
	\end{tabular}
	\label{tab:table}
\end{table}

>>>>

The full workflow for synthetic data can be reduced into four key steps:

\begin{itemize}
	\item \emph{Design}.
	\item \emph{Generation}.
	\item \emph{Evaluation}.
	\item \emph{Iteration}.
\end{itemize}

\subsection{Design}
\label{sec:worflowdesign}

@@

\subsection{Generation}
\label{sec:generation}

@@

\subsection{Evaluation}
\label{sec:evaluation}

@@

\subsection{Iteration}
\label{sec:iteration}

@@

Package detection

\begin{itemize}
	\item Background material and texture.
	\item Lighting intensity and positioning.
	\item Object material and texture.
	\item Number of objects in view.
\end{itemize}

\subsection{Domain Randomization}
\label{sec:domainrandomization}

Effect of domain randomized lighting

Effect of domain randomized backgrounds

\subsection{Training Curicculum}
\label{sec:curicculum}

Pre-training w/ real and fine-tuning on synthetic

Training only on synthetic

Training on mixed synthetic and real
